\providecommand\dbname{webshop}
\subsection{Create and load the postgresql database \dbname}

You must create a postgresql database named \Code{\dbname} and load it
with the initial data. To do that follow these steps:
\begin{enumerate*}\itemsep1pt\parskip0pt\parsep0pt
\item Open the database GUI pgadmin III.
\item Connect to the exam database. The user/role name is
  \textbf{exam} with password \textbf{exam}.
\item Open the \textit{servers} node, then open the server node \textit{exam}.
\item In the object browser (left panel with tree like structure)
  right-click on databases node in the tree and select \textbf{New database}
\item In the \textit{new Database} dialog enter \textbf{\dbname} in
  the name field and leave the rest to their defaults. Click Ok.
  \begin{itemize}
  \item Click on the \dbname database to activate the sql buttons.
  \end{itemize}
\item Select the execute sql button, the one with the magnifying
  glass.
\item Open the file browser (the folder icon).
\item In the folder \Code{\ldots/dbscripts/} you find the file
  {schema.sql}. Open, then execute it using the \textbf{ExecuteScript} button.
\item In the object browser, you can now verify that the script
  executed  successfully, by checking that the \dbname database exists
  and the tables, views and sequences as are defined in the
  script. 
\end{enumerate*}

When you want to restore the database to it's original state with a
filled inventory, you can re-execute the schema.sql script in
\textbf{pgAdmin III}.

% To make the jdbc driver available to the projects, you should
% first create a Netbeans Library, named as the one used in the project.
% See the assessment website for the exact details.
